Bounds on Coding Theory from Algebraic Geometry

### 2021-04-03 draft/draft.tex
Updates from Overleaf

\section{Singleton bound and a promising example} \label{s:singleton}
\begin{thm}[Singleton Bound]
If $C$ is a code with parameters $n, k, d$, then \[k + d \le n + 1,\] or equivalently, \[R + \delta \le 1 + 1/n.\]
\end{thm}
\begin{proof}

>>>>

\section{Singleton bound and a promising example} \label{s:singleton}
\begin{thm}[Singleton Bound]\label{thm:singleton_bound}
If $C$ is a code with parameters $n, k, d$, then \[k + d \le n + 1,\] or equivalently, \[R + \delta \le 1 + 1/n.\]
\end{thm}

\begin{prop}
Theorem \ref{thm:singleton_bound} holds for any linear code $C$.
\end{prop}

\begin{proof}
